Supplementary Information

### 2018-07-26 manuscript/supplement.tex
fixex figure in Appendix S5

  We combined published food webs from~\cite{GlobalWeb},~\cite{Riede2011},
  and~\cite{Dunne2013}. Of the 358 food webs available
  from~\cite{GlobalWeb}, 59 were rejected because their original source was
  unpublished or could not be retrieved. We further eliminated 13 source or
  sink webs (which describe feeding links flowing from or to a particular
  resource or top predator rather than the interactions of an entire
  community), 8 plant-pollinator webs, 33 host-parasitoid webs, and 2 networks
  describing competitive interactions. Finally, we eliminated 2 webs
  describing  inferred interactions in an extinct community, 10 ``generalised
  schemes'' that were not based on direct field data, and 4 webs where it was
  not clear which of several described study sites were used to construct the
  food web (and therefore the latitude of the food web could not be
  included). This left us with 226 webs from~\cite{GlobalWeb}.

  To these, we added 7 webs from~\cite{Dunne2013} that were originally used
  to assess the roles of parasites within food webs. As all but 3 of the webs
  from~\cite{GlobalWeb} contained only free-living species, we removed
  the parasites (and all interactions involving them) from these webs (and the
  3 webs containing parasites from~\cite{GlobalWeb}) leaving free-living
  species only. In addition, we included 30 of the 40 webs
  from~\cite{Riede2011}. Nine of the
  remaining webs in the~\cite{Riede2011} dataset were also included in
  the~\cite{GlobalWeb}  dataset, and the last web was derived from an
  unpublished source. This gave us a database of 263 webs. As a measure of
  quality-control, we then eliminated any food web which did not have at least
  one each of basal resources, intermediate consumers, and top predators. Webs
  which did not meet this requirement tended to be very small and poorly-resolved.
  Our final sample size was thereby reduced to 196 food webs.

  % Tree hole and pitcher plant webs counted as "lakes", wetlands could be either lakesor streams depending on the study

 See Table~\ref{S1} for a list of rejected webs and reasons for their
  exclusion.

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        123   & 3 & \cite{Harris1972}  & terrestrial & 40,45,28 N & Yes   &       \\
        124   & 3 & \cite{Collins1976}  & stream & 44,34 N & Yes   &       \\
        125   & 3 & \cite{Landry1977}  & marine &       & No    & Generalised scheme \\
        126   & 3 & \cite{Larsson1978}  & lake  & 61,26,00 N & Yes   &       \\
        127   & 3 & \cite{Beaver1979}  & lake  &       & No    & Could not locate original source \\
        128   & 3 & \cite{Beaver1979}  & lake  &       & No    & Could not locate original source \\
        129   & 3 & Unpublished & terrestrial &       & No    & Unpublished \\
        130   & 3 & \cite{Odum1975}  & estuary & 27,12 N & Yes   &       \\
        131   & 3 & \cite{Beaver1985}  & lake  & 4,12,37 N & Yes   &       \\
        132   & 3 & \cite{Beaver1985}  & lake  & 4,12,37 N & Yes   &       \\
        133   & 3 & \cite{Beaver1985}  & lake  & 7,52,22 N & Yes   &       \\
        134   & 3 & \cite{Beaver1985}  & lake  & 19 S  & Yes   &       \\
        135   & 3 & \cite{Beaver1985}  & lake  & 4,40,46 S & Yes   &       \\
        136   & 3 & \cite{Bradshaw1983}    & lake  &       & No    & Could not locate original source \\
        137   & 3 & \cite{Corker1984}  & lake  & 22,14-22,17 N & Yes   &       \\
        138   & 3 & \cite{Kitching1983}     & lake  &       & No    & Could not locate original source \\
        139   & 3 & \cite{Kitching1983}  & lake  &       & No    & Could not locate original source \\
        140   & 3 & \cite{Seifert1979}  & terrestrial & 10,21 N & Yes   &       \\
        141   & 3 & \cite{Seifert1976}  & terrestrial &       & No    & Competition network \\
        142   & 3 & \cite{Seifert1976}  & terrestrial &       & No    & Competition network \\
        143   & 3 & \cite{Snow1958}    & lake  & 34,41,45 N & Yes   &       \\
        144   & 3 & \cite{Snow1958}  & lake  &       & No    & Could not locate original source \\
        145   & 3 & \cite{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
        146   & 3 & \cite{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
        147   & 3 & \cite{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
        148   & 3 & \cite{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
        149   & 3 & \cite{Force1974}    & terrestrial &       & No    & Host-parasitoid web \\
        150   & 3 & \cite{Hopkins1984}     & terrestrial &       & No    & Host-parasitoid web \\
        151   & 3 & \cite{Richards1926}     & terrestrial & 51,20,04 N & Yes   &       \\
        152   & 3 & \cite{Whittaker1984}    & terrestrial &       & No    & Source web \\
        153   & 3 & \cite{Mayse1978}    & terrestrial & 40,06,38 N & Yes   &       \\
        154   & 3 & \cite{Mayse1978}    & terrestrial & 39,56,41 N & Yes   &       \\
        155   & 3 & \cite{Askew1975}     & terrestrial &       & No    & Host-parasitoid web \\
        156   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
        157   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
        158   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
         \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        337   & 3 & \cite{Alcorlo2001}  & lake  & 41,26,05 N & Yes   &       \\
        338   & 3 & \cite{Torres2013}  & marine &       & No    & Could not locate original source \\
        339   & 3 & \cite{Bulman2001}  & marine & 37-39 S & Yes   &       \\
        340   & 3 & \cite{Smith2007}  & marine & 74-78 S & Yes   &       \\
        341   & 3 & \cite{Lancraft1991}  & marine & 58,20.8 - 60,10.4 S & Yes   &       \\
        342   & 3 & \cite{Hopkins1993}  & marine & 57,00 - 60,45 S & Yes   &       \\
        343   & 3 & \cite{Kitching1987}  & lake  & 28,12 S & Yes   &       \\
        344   & 3 & \cite{Hodkinson2004}  & terrestrial &       & No    & Host-parasitoid web \\
        345   & 3 & \cite{Boit2012}  & lake  & 47,38,10 N & Yes   &       \\
        346   & 3 & \cite{Rayner2010}  & stream & 17,7 S & Yes   &       \\
        347   & 3 & \cite{Motta2005}  & stream & 23,03 S & Yes   &       \\
        348   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
        349   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
        350   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
        351   & 3 & \cite{Warren1989}     & lake  &       & No    & Could not locate original source \\
        352   & 3 & \cite{Poepperl2003}  & stream & 54,06 N & No    & describes compartments, not species \\
        353   & 3 & \cite{Poepperl2003}  & stream & 54,06 N & No    & describes compartments, not species \\
        354   & 3 & \cite{Goldwasser1993}  & terrestrial & 18,03 N & Yes   &       \\
        355   & 3 & \cite{Cohen2003}    & lake  & 46,13 N & Yes   &       \\
        356   & 3 & \cite{Cohen2003}    & lake  & 46,13 N & Yes   &       \\
        357   & 3 & \cite{Yodzis1998} & marine & 34,21 - 16 S & No    & Study site unclear \\
        358   & 3 & \cite{Schroter2003}  & terrestrial &       & No    & Generalised scheme \\
        359   & 3 & \cite{Baiser2012}  & lake  &       & No    & Study site unclear \\
        \hline
      \end{tabular}%
        }
    \end{table}%

  \end{landscape}
\newpage

@@

% \subsection*{Appendix S4: Scaling relationships by trophic level}

%   \subsubsection*{Methods}

%     We were also interested in the ways that scaling
%     relationships with species richness might
%     be affected by changes to the distribution of species 
%     among trophic levels. [[more justification of why]]
%     To that end, we repeated our 
%     analyses replacing species richness with the
%     proportion of basal resources, proportion of 
%     intermediate consumers, or proportion of top 
%     predators. All model fitting procedures were identical 
%     to those described for species richness. The model 
%     simplicication procedure was similar to
%     the procedure described for species richness, except 
%     that in some cases there were multiple models with 
%     $\delta$AIC\textless2 that shared the minimal degrees 
%     of freedom. In these cases, we defined the 
%     best-fitting model as the model with the lowest AIC in 
%     the set of models with $\delta$AIC\textless2 and the 
%     minimal degrees of freedom.

%   \subsubsection*{Results}

%     As with species richness, specialisation scaled with
%     the numbers and proportions of species at each trophic
%     level following a lognormal distribution.
%     The relationships between latitude and the proportions of species at each
%     trophic level were more complex than the flat relationship between latitude
%     and species richness in this dataset.  The proportion of basal resources
%     increased towards the poles in stream webs
%     ($\beta_{Latitude:stream}$=0.011, $p$\textless0.001)  but did not vary
%     with latitude in estuarine, marine, lake, or terrestrial  food webs
%     ($\beta_{Latitude}$=0.001, $p$=0.080), while the proportion of
%     intermediate consumers decreased towards the poles in all ecosystem types
%     except lakes ($\beta_{Latitude}$=-0.003, $p$=0.015 and
%     $\beta_{Latitude:Lake}$=0.005, $p$=0.016). The proportion of top predators
%     in a food web,  meanwhile, decreased towards the poles in lake and  stream
%     food webs but did not vary in other ecosystem types
%     ($\beta_{Latitude}$=0.002, $p$=0.151;  $\beta_{Latitude:Lake}$=-0.006,
%     $p$=0.001; and $\beta_{Latitude:stream}$=-0.007, $p$=0.006).

%     Unlike species richness, only generality showed an overall increase with
%     increasing proportions of basal resources in a web ($\beta_0$=0.019,
%     $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
%     link density, generality, and vulnerability, respectively;
%     Fig.~\ref{TL_rescaled}). In each case, however, there were substantial
%     effects of latitude on the scaling relationships. Thus, the scaling
%     exponents for link density and vulnerability were negative for estuarine,
%     lake, and stream communities and became more negative towards the poles
%     ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
%     $p$\textless0.001, respectively; Fig.~\ref{B}). For the scaling of link
%     density and vulnerability in marine and terrestrial communities, the overall
%     effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
%     $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
%     $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
%     $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
%     that there was weak scaling at most latitudes. In contrast, the scaling
%     exponent of generality with the proportion of basal resources was positive
%     near the equator and negative near the poles in estuarine, lake, and stream
%     communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
%     very little change in the scaling exponents for marine and terrestrial
%     communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
%     $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).

%     As with species richness, link density, generality, and vulnerability
%     generally increased with the proportion of intermediate consumers in a web
%     ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
%     $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{TL_rescaled}). 
%     The best-fit models for link density and vulnerability did not include
%     any effect of latitude. In contrast, the strength of the scaling relationship
%     for generality increased weakly towards the poles in estuarine, marine, and
%     terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
%     towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
%     and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{I}).

%     In contrast to the generally positive scaling relationships above, link
%     density, generality, and vulnerability decreased as the proportion of top
%     predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
%     $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
%     Fig~\ref{TL_rescaled}). For estuarine, lake, and marine food webs the
%     strength of this scaling did not vary significantly with latitude
%     ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
%     $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
%     In stream and terrestrial food webs, however, scaling was more strongly negative in the 
%     tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
%     and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
%     $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
%     for vulnerability; Fig.~\ref{T}. The best-fit model for generality did not include any terms
%     for latitude in any ecosystem type.

@@

\begin{figure}[!h]
\centerline{\includegraphics*[height=.75\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts_observed.eps}}
\caption{Scaling relationships for link density, generality, 
and vulnerability relative to species richness of a food web. 
For each relationship, we show observed values (white circles) and 
a simplified form of the scaling relationship described in equation 2 (\emph{Main Text}), neglecting 
any effects of habitat type or latitude (black line, N=196 food webs). See Fig. 1 (\emph{Main Text}) to compare with 
observed values correcting for the effects of habitat type and latitude. }
\label{props_v_lat_obs}
\end{figure}

% \newpage

% \begin{figure}[!h]
% \centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/TL_fitlines_nonts.eps}}
% \caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
% relative to the proportions of basal resources, intermediate consumers, and top predators in a food web. 
% Link density, generality,
% and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
% type. As these relationships take the form of power laws, we did this by dividing the food-web
% property (e.g. link density) by species richness raised to an exponent including the 
% effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
% type and latitude. Note that in all cases estuarine food webs were treated as the baseline 
% ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
% latitude retained in the best-fit model (see \emph{Results} for specifics). For each relationship, 
% we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
% ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
% see Fig.~\ref{TL_observed}.}
% \label{TL_rescaled}
% \end{figure}

% \newpage

% \begin{figure}[!h]
% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/scaling_with_S/proportions/TL_fitlines_nonts_observed.eps}}
% \caption{Scaling relationships for link density, generality, 
% and vulnerability relative to the proportions of basal resources, intermediate consumers, and top predators in a food web. 
% For each relationship, we show observed values (white circles) and 
% a simplified form of the scaling relationship described in equation 2 (\emph{Main Text}), neglecting 
% any effects of habitat type or latitude (black line, N=196 food webs). See Fig.~\ref{TL_rescaled} to compare with 
% observed values correcting for the effects of habitat type and latitude. }
% \label{TL_observed}
% \end{figure}

% \newpage

% \begin{figure}[!h]
% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}}
% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
% types and over latitude. For each property we show the scaling exponent for the proportion of
% basal resources (black line) with its 95\% confidence interval (in grey), based on N=196 
% empirical food webs. Latitude is given in degrees
% from the equator regardless of direction.}
% \label{B}
% \end{figure}

% \begin{figure}[!h]
% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
% types and over latitude. For each property we show the scaling exponent for the proportion of
% intermediate consumers (black line) with its 95\% confidence interval (in grey), based on 
% N=196 empirical food webs. Latitude is given in degrees
% from the equator regardless of direction.}
% \label{I}
% \end{figure}

% \newpage

% \begin{figure}[!h]
% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}}
% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
% types and over latitude. For each property we show the scaling exponent for the proportion of
% top predators (black line) with its 95\% confidence interval (in grey), based on N=196 
% empirical food webs. Latitude is given in degrees
% from the equator regardless of direction.}
% \label{T}
% \end{figure}

>>>>

  We combined published food webs from~\cite{GlobalWeb},~\cite{Riede2011},
  and~\cite{Dunne2013}. Of the 358 food webs available
  from~\cite{GlobalWeb}, 58 were rejected because their original source was
  unpublished or could not be retrieved. We further eliminated 13 source or
  sink webs (which describe feeding links flowing from or to a particular
  resource or top predator rather than the interactions of an entire
  community), 8 plant-pollinator webs, 33 host-parasitoid webs, and 2 networks
  describing competitive interactions. Additionally, we eliminated 2 webs
  describing  inferred interactions in an extinct community, 2 webs describing compartments rather than particular species,
  11 ``generalised
  schemes'' that were not based on direct field data, and 4 webs where it was
  not clear which of several described study sites were used to construct the
  food web (and therefore the latitude of the food web could not be
  included). This left us with 226 webs from~\cite{GlobalWeb}.

  To these, we added 7 webs from~\cite{Dunne2013} that were originally used
  to assess the roles of parasites within food webs. As all but 3 of the webs
  from~\cite{GlobalWeb} contained only free-living species, we removed
  the parasites (and all interactions involving them) from these webs (and the
  3 webs containing parasites from~\cite{GlobalWeb}) leaving free-living
  species only. In addition, we included 30 of the 40 webs
  from~\cite{Riede2011}. Nine of the
  remaining webs in the~\cite{Riede2011} dataset were also included in
  the~\cite{GlobalWeb}  dataset, and the last web was derived from an
  unpublished source. This gave us a database of 263 webs. 
  Some of these webs, as published, contained errors in species names or other formatting errors. We corrected these errors in order to match species arrayed along rows and columns (details in Table~\ref{S2}). As a measure of
  quality-control, we then eliminated any food web which did not have at least
  one each of basal resources, intermediate consumers, and top predators. Webs
  which did not meet this requirement tended to be very small and poorly-resolved.
  Our final sample size was thereby reduced to 225 food webs.
  % Tree hole and pitcher plant webs counted as "lakes", wetlands could be either lakesor streams depending on the study

 See Table~\ref{S1} for a list of rejected webs and reasons for their
  exclusion. 
  \clearpage

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        123   & 3 & \cite{Harris1972}  & terrestrial & 40,45,28 N & Yes   &       \\
        124   & 3 & \cite{Collins1976}  & stream & 44,34 N & Yes   &       \\
        125   & 3 & \cite{Landry1977}  & marine &       & No    & Generalised scheme \\
        126   & 3 & \cite{Larsson1978}  & lake  & 61,26,00 N & Yes   &       \\
        127   & 3 & \cite{Beaver1979}  & lake  &       & No    & Could not locate original source \\
        128   & 3 & \cite{Beaver1979}  & lake  &       & No    & Could not locate original source \\
        129   & 3 & Unpublished & terrestrial &       & No    & Unpublished \\
        130   & 3 & \cite{Odum1975}  & estuary & 27,12 N & Yes   &       \\
        131   & 3 & \cite{Beaver1985}  & lake  & 4,12,37 N & Yes   &       \\
        132   & 3 & \cite{Beaver1985}  & lake  & 4,12,37 N & Yes   &       \\
        133   & 3 & \cite{Beaver1985}  & lake  & 7,52,22 N & Yes   &       \\
        134   & 3 & \cite{Beaver1985}  & lake  & 19 S  & Yes   &       \\
        135   & 3 & \cite{Beaver1985}  & lake  & 4,40,46 S & Yes   &       \\
        136   & 3 & \cite{Bradshaw1983}    & lake  &       & No    & Could not locate original source \\
        137   & 3 & \cite{Corker1984}  & lake  & 22,14-22,17 N & Yes   &       \\
        138   & 3 & \cite{Kitching1983}     & lake  &       & No    & Could not locate original source \\
        139   & 3 & \cite{Kitching1983}  & lake  &       & No    & Could not locate original source \\
        140   & 3 & \cite{Seifert1979}  & terrestrial & 10,21 N & Yes   &       \\
        141   & 3 & \cite{Seifert1976}  & terrestrial &       & No    & Competition network \\
        142   & 3 & \cite{Seifert1976}  & terrestrial &       & No    & Competition network \\
        143   & 3 & \cite{Snow1958}    & lake  & 34,41,45 N & Yes   &       \\
        144   & 3 & \cite{Snow1958}  & lake  &       & No    & Could not locate original source \\
        145   & 3 & \cite{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
        146   & 3 & \cite{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
        147   & 3 & \cite{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
        148   & 3 & \cite{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
        149   & 3 & \cite{Force1974}    & terrestrial &       & No    & Host-parasitoid web \\
        150   & 3 & \cite{Hopkins1984}     & terrestrial &       & No    & Host-parasitoid web \\
        151   & 3 & \cite{Richards1926}     & terrestrial & 51,20,04 N & Yes   &       \\
        152   & 3 & \cite{Whittaker1984}    & terrestrial &       & No    & Source web \\
        153   & 3 & \cite{Mayse1978}    & terrestrial & 40,06,38 N &   &     \\
        154   & 3 & \cite{Mayse1978}    & terrestrial & 39,56,41 N &   &     \\
        155   & 3 & \cite{Askew1975}     & terrestrial &       & No    & Host-parasitoid web \\
        156   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
        157   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
        158   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
         \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        337   & 3 & \cite{Alcorlo2001}  & lake  & 41,26,05 N & Yes   &       \\
        338   & 3 & \cite{Torres2013}  & marine &       & No    & Could not locate original source \\
        339   & 3 & \cite{Bulman2001}  & marine & 37-39 S & Yes  &     \\
        340   & 3 & \cite{Smith2007}  & marine & 74-78 S & Yes   &       \\
        341   & 3 & \cite{Lancraft1991}  & marine & 58,20.8 - 60,10.4 S & Yes   &       \\
        342   & 3 & \cite{Hopkins1993}  & marine & 57,00 - 60,45 S & Yes  &     \\
        343   & 3 & \cite{Kitching1987}  & lake  & 28,12 S & Yes   &       \\
        344   & 3 & \cite{Hodkinson2004}  & terrestrial &       & No    & Host-parasitoid web \\
        345   & 3 & \cite{Boit2012}  & lake  & 47,38,10 N & Yes  &     \\
        346   & 3 & \cite{Rayner2010}  & stream & 17,7 S & Yes   &       \\
        347   & 3 & \cite{Motta2005}  & stream & 23,03 S & Yes   &       \\
        348   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
        349   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
        350   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes  &     \\
        351   & 3 & \cite{Warren1989}     & lake  &       & No    & Could not locate original source \\
        352   & 3 & \cite{Poepperl2003}  & stream & 54,06 N & No    & describes compartments, not species \\
        353   & 3 & \cite{Poepperl2003}  & stream & 54,06 N & No    & describes compartments, not species \\
        354   & 3 & \cite{Goldwasser1993}  & terrestrial & 18,03 N & Yes   &       \\
        355   & 3 & \cite{Cohen2003}    & lake  & 46,13 N & Yes   &       \\
        356   & 3 & \cite{Cohen2003}    & lake  & 46,13 N & Yes   &       \\
        357   & 3 & \cite{Yodzis1998} & marine & 34,21 - 16 S & No    & Study site unclear \\
        358   & 3 & \cite{Schroter2003}  & terrestrial &       & No    & Generalised scheme \\
        359   & 3 & \cite{Baiser2012}  & lake  &       & No    & Study site unclear \\
        \hline
      \end{tabular}%
        }
    \end{table}%
  \end{landscape}

  \clearpage

  \clearpage
  \begin{center}
    \begin{table}[h!]
      \caption{Networks with corrections. Names are as in Table S1. All corrected webs were taken from~\cite{GlobalWeb}. Some links were coded as negative values, decimal values, or values other than 1 that were intended to convey additional information. All were re-coded as 1. In a few cases, entries of -1 indicated links that should not be included in the network (e.g., where primary producers would be interpreted as predators). These entries were changed to 0. Some webs contained missing column or row labels; these were inferred based on species ordering in the complete dimension. Some row or column labels contained sample sizes or life stage information missing from the other dimension, or contained typos in either row or column labels. These were removed such that row and column labels matched. In most webs, predators were given across columns and prey down rows. Where this was not the case, rows and columns were flipped.}
      \label{S2}
      {\footnotesize
      \begin{tabular}{l | p{13cm}}
      Web ID & Type of correction \\
      \hline
      18 & Corrected -1 entry to 1 \\
      22 &  Corrected -1 entries to 1, -2 entries to 0 \\
      23 & Corrected -1 entries to 1 \\
      24 &  Corrected -1 entries to 1 \\
      26 & Corrected decimal entries to 1, -1 entries to 1 \\
      33 & Corrected decimal entries to 1 \\
      37 & Corrected -1 entries to 1 \\
      38 & Converting -1 entries to 1 \\
      39 & Corrected species names \\
      41 & Corrected species names \\
      60 & Corrected species names \\
      80 & Corrected species names \\
      114 & Corrected -1 entry to 1 \\
      117 & Corrected -1 entry to 1 \\
      119 & Corrected -1 entries to 1 \\
      120 & Corrected -1 entries to 1 \\
      153 & Corrected -1 entries to 1 \\
      154 & Corrected -1 entries to 1  \\
      180 &  Corrected entries indicating a primary producer as predator to 0 \\
      181 &  Corrected -1 entries to 1 \\
      182 &  Corrected -1 entries to 1 \\
      183 &  Corrected -1 entries to 1 \\
      202 &  Corrected -1 entries to 1  \\
      213 &  Corrected -1 entries to 1  \\
      214 &  Corrected species names \\
      215 &  Corrected species names \\
      216 &  Corrected species names \\
      217 &  Corrected species names \\
      218 &  Corrected species names \\
      219 &  Corrected species names \\
      220 &  Corrected species names \\
      221 &  Corrected species names \\
      222 &  Corrected species names \\
      223 &  Corrected species names \\
      224 &  Corrected species names \\
      225 &  Corrected species names \\
      \hline
      \end{tabular} }
      \end{table}

      \begin{table}
      {\footnotesize
      \begin{tabular}{l | p{13cm}}
      Web ID & Type of correction \\
      \hline
      236 &  Corrected informative entries to 1; corrected species names \\
      238 &  Corrected informative entries to 1 \\
      240 &  Corrected informative entries to 1 \\
      244 &  Corrected informative entries to 1 \\
      246 &  Corrected informative entries to 1 \\
      249 &  Corrected decimal entries to 1 \\
      250 &  Corrected decimal entries to 1 \\
      251 &  Corrected decimal entries to 1 \\
      252 &  Corrected decimal entries to 1 \\
      253 &  Corrected decimal entries to 1 \\
      254 &  Corrected decimal entries to 1 \\
      255 &  Corrected decimal entries to 1 \\
      256 &  Corrected decimal entries to 1 \\
      257 &  Corrected decimal entries to 1 \\
      258 &  Corrected decimal entries to 1 \\
      259 &  Corrected decimal entries to 1 \\
      260 &  Corrected decimal entries to 1 \\
      261 &  Corrected decimal entries to 1 \\
      262 &  Corrected decimal entries to 1 \\
      265 &  Corrected decimal entries to 1 \\
      266 &  Corrected decimal entries to 1 \\
      267 &  Corrected decimal entries to 1 \\
      268 &  Corrected decimal entries to 1 \\
      269 &  Corrected decimal entries to 1 \\
      288 &  Corrected decimal entries to 1 \\
      289 &  Corrected decimal entries to 1 \\
      290 &  Corrected quantitative entries to 1 \\
      291 &  Corrected quantitative entries to 1 \\
      292 &  Corrected quantitative entries to 1 \\
      293 &  Corrected quantitative entries to 1 \\
      294 &  Corrected decimal entries to 1; flipped rows and columns \\
      296 &  Corrected decimal entries to 1 \\
      307 &  Corrected decimal entries to 1 \\
      320 &  Corrected decimal entries to 1 \\
      321 &  Corrected decimal entries to 1 \\
      322 &  Corrected decimal entries to 1 \\
      323 &  Corrected decimal entries to 1 \\
      324 &  Corrected decimal entries to 1 \\
      333 &  Corrected species names; corrected - entries to 1, + entries to 0, +/- entries 10 1; flipped rows and columns \\
      339 &  Corrected decimal entries to 1; corrected species names \\
      342 &  Corrected quantitative entries to 1; corrected species names \\
      345 &  Corrected quantitative entries to 1 \\
      350 &  Corrected quantitative entries to 1 \\
      351 &  Corrected quantitative entries to 1 \\
      357 &  Corrected quantitative entries to 1 \\
      359 &  Corrected species names \\
      \hline
      \end{tabular} }
    \end{table}
  \end{center}
\clearpage

@@

\clearpage

@@

  \begin{figure}[!h]
  \centerline{\includegraphics*[height=.75\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts_corrected_observed_corrected.eps}}
  \caption{Scaling relationships for link density, generality, 
  and vulnerability relative to species richness of a food web. 
  For each relationship, we show observed values (white circles) and 
  a simplified form of the scaling relationship described in equation 2 (\emph{Main Text}), neglecting 
  any effects of habitat type or latitude (black line, N=196 food webs). See Fig. 1 (\emph{Main Text}) to compare with 
  observed values correcting for the effects of habitat type and latitude. }
  \label{props_v_lat_obs}
  \end{figure}
